% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex




\chapter{Anisothermal sheath}
\label{ch-3}

In order to explain the discrepancy observed in \cref{ch-2} between the simulation and the sheath model, we investigate the simulation data.
We see that the hypothesis of the sheath model do not stand.
Using a simplified \ac{1D} \ac{PIC} simulation, we derive a polytropic closure for the electron.
With this new closure equation, we derived a modified sheath model, that fit well the kinetic simulations. 

% 
% {\bf III. Polytrotic sheath model} 23 pages
% \begin{zzz}
%   This chapter takes the 2nd paper about the modified sheath model
% 
%   3.1 EVDF in the 2D PIC simulations of HET.    3 pages
% 
%   3.2 1D simplified simulations, Parametric study and polytropic fits. 7 pages
% 
%   3.3 Monte-Carlo simulations.  3 pages
% 
%   3.4 fluid equations with polytropic closure. 10 pages
% \end{zzz}


\minitoc

\Cref{ch-2} has showed us a discrepancy between the expected plasma-wall interaction quantities -- as the plasma potential drop thought the sheath and the electron emission rate -- and the \ac{PIC} simulation results.
These discrepancies are expected to explain the difficulties of the community to model the discharge (see for example \citet{croes2017} section 5.4 and \citet{raitses2011}).
Hence, a better understanding of the plasma-wall interaction observed is required.

In this chapter, we come back to the simulation results presented in \cref{ch-2}  in order to gather more insights on the plasma-wall interaction.
Then, we develop a simplified simulation in order to isolate the plasma-wall interaction from the rest of the phenomena.
This second simulation is unidirectional (\acs{1D}-\acs{3V}), un-magnetized, and without electron emission.
From this simplified simulation, we derived an anisothermal sheath model, that described well the kinetic simulations.
We extend the model to the case where ionization is self-consistent.


\input{Chapitre3/31-Insights}
\input{Chapitre3/32-1DPIc}
\input{Chapitre3/33-kinetic}
\input{Chapitre3/34-MCM}
\input{Chapitre3/35-fluid_model}
\input{Chapitre3/36-conclusion}

