% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex




\chapter{Particle-In-Cell simulations of Hall Effect Thrusters}
\label{ch-1}
Structure :

{\bf Particle in Cell simulations} 20 pages
\begin{zzz}
  
  1.1 The HET
  1.2 Elements of the 2D PIC-MCC simulations

  1.3 Numerical implementation

  1.4 R-theta simulation: hypotheses
  
  1.5 focus on  Dielectrics : Poisson equation 

  1.6 Axial convection model
  
  1.7 Conclusion
\end{zzz}
\inlinenote{Is missing a part of the HET physics. Like the Boeuf Tutorial. }
\inlinenote{Missing SEE }

The \ac{HET} has been studied since its first designs int he 1960's.
However, the physical processes the govern its behaviour stay ill-understood.
For most of them, as the electron cross field mobility or the plasma-surface interactions, kinetic informations are needed.

\paragraph{Kinetic informations}
Usually, we use "kinetic" in contrast to the "fluid" description of a fluid or plasma.
In the fluid descriptions, the density, mean velocity and temperature are used to describe the system.
However, the fluid is constituted of a myriad of particle.
We can describe the particles inside an elementary volume by their velocity distribution.
The three first moment moment of the distribution are actually the density (\nth{0} moment), the velocity (\nth{1} moment) and the temperature (\nth{2} moment).
Equations and simulations dealing with the velocity distribution of the particles are named kinetic.

\ac{PIC} - \ac{MCC} simulations are one of the two main ways to conduct kinetic simulations, with the Vlasov solver, also known as \ac{DK} simulations.
While the \ac{DK} simulations using an Eulerian description of the position and velocity space, \ac{PIC} simulations uses an Lagrangian approach.

The next section present the basics of the \ac{PIC} - \ac{MCC} simulations, and the simulations code \LPPic that is develop at \ac{LPP}.


\inlinenote{add SEE models, discussions concerning the choice we did, a.s.o.}
 
% \input{Chapitre1/11_HET}
% \input{Chapitre1/11_elements}
% \input{Chapitre1/12_2D_domain}
% \input{Chapitre1/13_Dielectric}
% \input{Chapitre1/14_convection}
% \input{Chapitre1/15_conclusion}
