% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex

\section{Study of electron cross field transport with a 2D radial-azimuthal PIC simulation}
  \label{sec-transport}
  

  A key topic of my PhD work is to study the impact of surface processes on the plasma discharge and in particular on the electron mobility.   
  The electron mobility in the axial direction $\mobe$ is defined as the ratio between the mean velocity $u$ and the electric field
  \begin{equation} \label{eq-mudef}
    \mobe = \frac{u_{e,z}}{E_z}
  \end{equation}
  with $u_{e,z}=<v_{e,z}>$ the electron mean velocity.
  \nomenclature[Q]{\ensuremath{ u_{e,z}}}{Electron mean velocity in the axial direction\string: $u_{e,z} = < v_{e,z}>$}
  In the \ac{PIC} simulations, \cref{eq-mudef} can be used directly to compute $\mobpic$.
  As introduced before, in the \ac{PIC} simulation the velocity is shifted by half a time step compared to the position.
  Thus, a special attention must be given in to compute $\mobpic$.
  
  In the classical drift diffusion theory of the electron mobility transverse to a magnetic field, the mobility is due to collisions as seen in \cref{eq-mobility} 
  \begin{equation} \label{eq-mobclas}
    \mobcla = \frac{e}{m_e} \frac{\nu_m}{\nu_m^2 + \oce^2}
  \end{equation}
  with $\oce=\frac{e B}{m_e}$ the electron cyclotron frequency and $\nu_m$ the electron-neutral momentum transfer collision frequency.
  In order to evaluate \cref{eq-mobclas},  $\nu_m$ is measured in the \ac{PIC} simulations at every cell.
  The mobility induced by the instability when neglecting the collision , as introduced in \cref{sec-mob}, is 
  \begin{equation} \label{eq-eq_mobeffsimple_two}
      \mobeff = \frac{< \dne \dEt >_{\theta} }{n_0 E_z}   \frac{1}{B_r}
  \end{equation}
  The correlation term $< \dne \dEt >_{\theta}$ can be computed in the \ac{PIC} simulation at every radial position.
  Using its radial profile, we will be able to determine where the instability enhances the electron mobility the most.
  
  In  \citet{lafleur2016}, the authors present the instability effect as an electron-ion friction force $\Rei = - e < \dne \dEt >_{\theta}$.
  Under the assumption that the saturation of the instability is mainly due to ion trapping, the electron-ion friction force can be simplified in the \ac{2D} geometry of the simulation to
  \begin{equation} \label{eq-rei-sat}
    \Rei^{sat} = \frac{e \norm{\grad \cdot (n_e \Te \vect{v_i})}}{4 \sqrt{6} c_s} \simeq \frac{e n_e \Te \viout}{4 \sqrt 6 c_s L_z}
  \end{equation} 
  \nomenclature[Q]{\ensuremath{ \vect{v_i}}}{  ion velocity vector}
  \nomenclature[Q]{\ensuremath{ c_s}}{ ion sound speed $c_s=(e \Te/m_i)^{1/2}$ }
  where $\vect{v_i}$ is the ion velocity, $c_s=(e \Te/m_i)^{1/2}$  is the ion sound speed, and the spatial derivative has been approximated across the axial simulation direction, with $\viout$ the ion outlet velocity 
  \begin{equation} \label{eq-viz}
    \viout = \sqrt{\frac{2 e U_z}{m_i}},
  \end{equation}
  with $U_z = E_z L_z$ the total potential difference in the axial direction.
  \nomenclature[Q]{\ensuremath{ U_z}}{   total potential difference in the axial direction $U_z = E_z L_z$}
  
  Using \cref{eq-rei-sat} in \cref{eq-mobeffsimple}, we obtain the simplified expression of the effective mobility at saturation
  \begin{equation} \label{eq-mobeffsat}
    \mobeffsat = \frac{\sqrt{\frac{\Te}{U_z}}}{4\sqrt{3}B_r}.
  \end{equation}
  
  \Cref{eq-mobeffsat} shows that for the radial and azimuthal \ac{2D} geometry being used here, the enhanced mobility due to \ac{ECDI} scales as the square-root of the electron temperature $\Te$ if the simulation parameters are constant.
  However, it is not the case in general, as the saturation of the instability can be also be due to convection, and there are axial gradients in the electron temperature and plasma density as well.
  
  We can note that $\mobpic, \mobeff$ and $\mobcla$ are defined at every position of the simulation, but that $\mobeffsat$ can only be globally calculated. 
  
  
  
  
  