% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex

\section{Sheath model with electron emission}
  \label{sec-sheath}
  
  \inlinenote{Ici, le model est introduit rapidement... Peut-etre le faire plus explicitement a partire des equations fluid ?}
  
  The sheath model featuring SEE processes has been historically studied by Hobbs and Wesson \citet{hobbs1967}, but is still an active research topic nowadays \citep{ahedo2005}.
  The sheath is often considered to be collision-less and isothermal, while the plasma is composed of hot Maxwellian electrons and cold ions. A third population of electron-induced secondary electrons is also present in the sheath, and the re-emission rate $\rate$ is assumed to be constant.
  The SEE process modifies the potential drop in the sheath as \citep{hobbs1967}
  \begin{equation} \label{eq-sheathhobbs}
    \dphisheath = \Tepar \ln \lp (1 - \rate) \sqrt{\frac{m_i}{2 \pi m_e}}   \rp
  \end{equation}
  with $\Tepar$ the electron temperature in the direction parallel to the magnetic field, thus normal to the walls.
  Adding a pre-sheath drop of $\Tepar/2$ \citep{ahedo2002}, the total potential drop to the wall becomes
  
  \begin{equation} \label{eq-total_drop}
    \dphi = \dphisheath + \frac{\Tepar}{2} =  \Tepar \lp \frac{1}{2} + \ln \lb (1 - \rate) \sqrt{\frac{m_i}{2 \pi m_e}}   \rb  \rp
  \end{equation}
  
  In \Cref{eq-sheathhobbs,eq-total_drop}, we uses $\Tepar$ as in general, and more precisely for low-pressure magnetized plasma, the electrons can be anisotrope.
  
  We can see that \cref{eq-sheathhobbs} becomes negative for a critical value of the emission rate
  \begin{equation} \label{eq-ratecrone}
    \rate_{\rm max} = 1 - \sqrt{\frac{2 \pi m_e}{m_i}} \simeq 0.985 \text{ for Xenon.}
  \end{equation}
  
  However, before that $\rate$ attains $\rate_{\rm max}$, the model of \citet{hobbs1967} presents another behaviour against the hypotheses of  \cref{eq-sheathhobbs}, as the sheath becomes \ac{SCL}.
  In the \ac{SCL} conditions, the electron emission is so large that the electric field at the wall becomes zero 
  \begin{equation} \label{eq-scl_Er}
    \deriv{\phi}{r} \at{\rm wall}= 0 
  \end{equation}
  In this case, the plasma potential drop to the wall for any ion mass is \citep{hobbs1967}
  \begin{equation} \label{eq-dphi_scl}
    \dphiscl \simeq 1.02 \Tepar,
  \end{equation}
  and the limit emission rate is
  \begin{equation} \label{eq-ratecr}
    \ratecr \simeq 1 - 8.3 \sqrt{\frac{m_e}{m_i}}
  \end{equation}

  For xenon, \cref{eq-ratecr} gives $\ratecr = 0.983$ \citep{goebel2008}.\footnote{This value of 0.983 is obtained after several approximation, as \cref{eq-scl_Er} , some of which should not allow to use three significant digits. That's why it does not exactly match with the numerical results presented in \cref{fig-potential_profile}.}

  \Cref{fig-potential_profile} illustrates the sheath model of \citet{hobbs1967} by showing the plasma potential profile in the sheath for different values of electron emission rate for a xenon plasma.
  \cref{fig-potential_profile}.{\bf a} gives the potential $\phi$ normalized by $\dphisheath$ from \cref{eq-sheathhobbs}, and \cref{fig-potential_profile}.{\bf b} gives $\phi$ not normalized.
  We can see in \cref{fig-potential_profile}  that for $\rate < \ratecr$, the plasma potential reached $\dphisheath$.
  However, for $\rate > \ratecr$, the plasma potential do not reaches $\dphisheath$, resulting in a non-zero current to the wall.
  Indeed, the sheath is not monotonic in this case, hence the hypotheses needed to develop \cref{eq-sheathhobbs} are not fulfilled.
  
  In \cref{fig-potential_profile}.{\bf b}, we can see that at $\rate \simeq \ratecr$, the plasma potential tends towards $\Te$, as mentioned by \cref{eq-dphi_scl}.
  \begin{figure}[hbtp]
    \centering
    \begin{tabular}{c c}
      \subfigure{plasma_profile_normed}{a}{25,20} & 
      \subfigure{plasma_profile}{b}{25,20} 
    \end{tabular}
    \caption{Evolution of the plasma potential in the sheath for different values of electron emission rate $\rate$ fro a xenon plasma, ({\bf a}) normalized by the total potential drop $\dphisheath$ from \cref{eq-sheathhobbs}, and ({\bf b}) normalized by the electron temperature, but $\dphisheath/\Te$ is noted with the black dotted line.  }
    \label{fig-potential_profile}
  \end{figure}
  
  