% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex




\chapter{Azimuthal instability}
\label{ch-5}

\begin{Chabstract}
  
As briefly mentioned in \cref{ch-1}, the $E \times B$ configuration of the \ac{HET} give rise to azimuthal instabilities.
This aspect has been neglected in \cref{ch-2,ch-3}, except by they consequences on the axial electron transport.
While these instabilities are the subject of numerous studied, they remain unclear.

Using the results of the \ac{PIC} simulations, we propose new insights for the understanding on the instability, hence the electron cross-field transport.
In particular, we develop a relation dispersion solver that uses the velocity distribution function measured in the simulations.
Then, we compare the simulation instability characteristics with the dispersion relations.
A special care is taken with the boundary condition and the instability non-linear saturation. 
\end{Chabstract}

% 
% 
% {\bf V. analyse of the instability } 30 pages
% \begin{zzz}
%   \begin{itemize}
% \item Instability dispersion relation
% \item Kinetic solver for Ion and ECDI using VDFs
% \item Impact of the difference w/r Maxwellian
% \item Wall Boundary condition, 3D dispertion relation vs 1D and 2D relations
% \item Linear stage as ECDI and Saturation toward IAW
% \end{itemize}
% \end{zzz}

\minitoc


The presence of azimuthal instabilities in the Hall effect thrusters has first been showed with numerical simulations by \citet{adam2004}.
However, their nature is not yet clear.
The investigation of the instabilities observed in the \ac{2D} \ac{PIC} simulations in the subject of this chapter.

In \cref{sec-PIC-ECDI}, we present the oscillations observed in the \ac{PIC} simulations.
After that, we derive the dispersion relation with no hypothesis used concerning the particle distribution functions in \cref{sec-DR-kinetic}, and we present in \cref{sec-DR-solver} a numerical algorithm that solves the dispersion relation using the distribution function measured in the \ac{PIC} simulations.
The oscillations observed in the simulation are compared in \cref{sec-DR-results} to the results of the dispersion relation.
To finish with; the impact of the radial boundary condition is investigated in \cref{sec-DR-BC}.

\input{Chapitre5/50-PICresults}
\input{Chapitre5/51-DR}
\input{Chapitre5/52-solver}
\input{Chapitre5/53-results}
\input{Chapitre5/54-radialBC}
\input{Chapitre5/55-conclusion}
