% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex




\chapter*{Acknowledgment}

The results presented here are a part of three years of somewhat difficult work, which would have not been possible without a lot of persons. 

Foremost, I would like to thank my advisors, Anne Bourdon and Pascal Chabert, for being such wonderful guides. 
You were always cheerful, and provided me with invaluable help.
I would also like to thank Vivien Croes, for motivating me to candidate to this project and for his help and friendship.
I would also like to acknowledge Stephan Zurbach for his trust.

This journey was accompanied by three dear fellow travelers, Florian Marmuse, Romain Lucken, and Thomas Charoy, whom I cannot thank enough.
I know you will have a strong impact, wherever you go and whatever you do.

I also want to acknowledge all those involved in this work.
Trevor Lafleur, for his amazing knowledge both in physics and simulation.
Alexis Jeandet and Nicolas Aunai, for all there expertise they shared without counting the time and the cost.
All the engineers that administrate the numerous computers I used: Zoidberg, thanks to Nicolas Marsac, but also Hopper, Occigen (CINES), and Nemo (CERFACS).

Furthermore, I used numerous Free and OpenSource software: all the operating system uses Linux, under several distrions; the simulation code was compiled with the Gnu compilers; the figures were made using Python and the wonderfull matplotlib package, and Inkspace was used for the illustrations; the manuscrit, reports and presentations were created using LaTex ; Atom is my text editor of predilection; and so many more tools that I cannot thank enough.

Lastly, I would like to thank my dear wife Audrey, for supporting me through all the ups, but mostly for the downs that accompanied this experience.
Her contribution was the most important for the success of this adventure.

