% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex

\section*{Scientific challenges of the HETs}
\addcontentsline{toc}{section}{Scientific challenges of the HETs}

The scientific challenges are the critical phenomena that are currently not understood enough and prevent the industrial development of \ac{HET}s.
As introduced before, in this Ph.D. manuscript, we focus on 2 of them : the electron transport and the plasma-wall interaction.


\subsection*{Electron drift and azimuthal instability in the HETs}
\addcontentsline{toc}{subsection}{Electron drift and azimuthal instability in the HETs}

The axial electric field $E$ and the radial magnetic field $B$ induces an azimuthal $E\times B$ drift of the electrons.
The drift velocity $v_{\rm d, ExB}$ is 
\begin{equation} \label{eq-exbdriftbis}
  v_{\rm d, ExB} = \bigg\lvert \frac{\vect{E} \times \vect{B}}{B^2} \bigg\rvert = \frac{E}{B} \sim \sn{1.5}{6} \,\meter\per\second
\end{equation}
Because of their large mass, the ions are not significantly affected by the magnetic field.
Hence they do not drift azimuthally.
As a consequence, there is a significant difference between the movement of electrons and ions in the azimuthal direction.

This drift of electrons relative to the ions leads to instability in the azimuthal directions, so some  authors refers the instabilities as \ac{EDI}.
However, as the drift is perpendicular to the magnetic field, it is subject to the cyclotron resonances.
Therefore, in this thesis we use the more precise second name for these instabilities, the \ac{ECDI}.
But it should be noted that both terms refer to the same physical phenomena.

The actual nature of the \ac{ECDI} remains unclear\citep{boeuf2018}, as the \ac{ECDI} characteristics are very close to usual \ac{IAW}, and that experimental measurements are challenging to conduct in the range of parameter of interest.
Hence, the community is still arguing about the actual nature of wave observed.
A part of the work undertaken during my thesis concerns the study and characterization of the instabilities observed in the kinetic simulations.
These instabilities are treated in \cref{ch-5}.


\subsection*{Cross-field transport of the elections}
\addcontentsline{toc}{subsection}{Cross-field transport of the elections}
  \label{sec-mob}
  
  As a first approximation, electrons are usually assumed to be frozen by the magnetic field and rotate only in the azimuthal direction due to the drift $E \times B$.
  But in fact, they present a so-called cross-field transport toward the anode in the axial direction.
  For instance because of collisions, the electrons can jump from one magnetic line to another.
  This leads to a transport in the direction of the electric field.
  This transport can be expressed considering the electron momentum conservation equation \citep{lafleur2016a}\string:
  \begin{align*} %\label{eq-elec_momentum_mobility}
    \partial_t(m_e n_e \vect{v}_{de}) + \div(m_e n_e  \vect{v}_{de} \vect{v}_{de})  = & q_e n_e ( \vect{E} + \vect{v}_{de} \times \vect{B})  &&\text{(Lorenz force)}\\ &- \div \vect{\Pi}_e &&\text{(pressure gradient)}\\ & - m_e \nu_m n_e \vect{v}_{de}, &&\text{(collisions)}
  \end{align*}
  where $m_e, q_e$, $n_e$, $\vect{v}_{de}$, and $\vect{\Pi}_e $ are the electron mass, charge, density, drift velocity and pressure tensor, and $\nu_m$ is the electron-neutral momentum transfer collision frequency.
  Ignoring the electron inertia and the pressure term, and with $\vect{B} = B_0 \vect{e}_r$, we can write the conservation equation projected on the axial and azimuthal direction
  \begin{equation} \label{eq-elec_momentum_mobility2}
  \begin{cases}
    0 =  n_e E_z - n_e v_{de{\theta}} B_0 - \frac{m_e}{q_e} \nu_m n_e v_{dez}\\
    0 =  n_e E_{\theta} -  n_e v_{dez} B_0 - \frac{m_e}{q_e} \nu_m n_e v_{de{\theta}}
  \end{cases}
  \end{equation}
  Supposing that there is no electric field in the azimuthal direction because of the azimuthal periodicity ($E_{\theta}=0$),  we can combine the two equations of \cref{eq-elec_momentum_mobility2} and have \citep{chen2006,meezan2001}
  \begin{equation} \label{eq-mobility}
    \mobcla = \frac{n_e v_{dez}}{n_e E_z} = \frac{ \frac{\norm{q}}{m \nu_m}}{1 + \frac{\oce^2}{\nu_m}}
  \end{equation}
  with $\oce= \frac{\norm{q}B_0}{m}$ the cyclotron frequency.
  \nomenclature[Q]{\ensuremath{ \oce}}{ Electron cyclotron frequency $\oce=\frac{e B}{m_e}$}
  \nomenclature[Q]{\ensuremath{ \nu_m}}{  Electron-neutral momentum transfer collision frequency}
  \nomenclature[Q]{\ensuremath{ \mu}}{  Electron mobility, such that $v_e = \mu E$}
  \nomenclature[Q]{\ensuremath{ \mobcla}}{ Classical electron mobility, defined in \cref{eq-mobility}}
  At the exit plane, the classical mobility predicts a mobility of the order of $\mobcla=0.001-0.01\mobunit$ \citep{adam2008a}.
    
  However, it has been observed in experiments by \citet{meezan2001} that the electron cross-field transport in the axial direction of the \ac{HET} is higher than $\mobcla$.
  Different phenomena have been proposed to explain the origin of this \emph{anomalous} transport.
  Two phenomena are supposed to be mainly responsible for this enhanced mobility \citep{croes2017}\string: the azimuthal instability and the near-wall mobility due to electron emission.
  A significant part of the work of this Ph.D. thesis concerns the quantitative comparison of the relative importance of the two phenomena.
  
  The mobility induced by the azimuthal instability has first been observed in \ac{PIC} simulations by \citet{adam2004}, since then, it has been reproduced several times \citep{adam2008a,heron2013,lafleur2016a,croes2017,boeuf2018,taccogna2019}.
  The kinetic approach allowed \citet{lafleur2016a} to propose a modified mobility due to the oscillations of the electron density and the azimuthal electric field of the \ac{ECDI}.
  This effective mobility obtained is 
  \begin{equation} \label{eq-defmobeff}
    \mobeff = \mobcla \lp 1 - \frac{\oce}{\nu_m}  \frac{< \dne \dEt >_{\theta} }{n_0 E_z}   \rp
  \end{equation}
  with \dne{} and \dEt{} the fluctuations in the azimuthal directions of the electron density and azimuthal electric field, respectively, the operator $< . >_{\theta}$ is the average in the azimuthal direction, and $n_0$ is the average plasma density.
  In the case where $\nu_m << \oce$, \cref{eq-defmobeff} can be simplified to 
  \begin{align} 
    \mobeff &= \frac{\frac{e}{m_e} \nu_m}{\oce^2} \lp 1 - \frac{\oce^2}{\nu_m}  \frac{< \dne \dEt >_{\theta} }{n_0 E_z}   \rp \nonumber \\
    &= \frac{< \dne \dEt >_{\theta} }{n_0 E_z}   \frac{1}{B_r} \label{eq-mobeffsimple}
  \end{align}
  which shows that the instability enhances the electron axial mobility in a way similar to an $E \times B$ drift.
  The electric field $E_{\theta}$ oscillates and presents a zero mean value, but the average effect on the electron transport is not zero if the correlation between \dEt{} and \dne{} is not zero.
  
  The amplitude of the instability at steady-state depends on the saturation mechanisms and the convection of the wave.
  Studies have been  undertaken very recently but more work is still needed to derive expressions of the effective cross-field mobility that could be used in fluid models \citep{boeuf2017}.
  Another approach has been recently proposed by \citet{jorns2018}.
  The author compared the experimental measurements of four different \ac{HET} with a radial-axial fluid code, Hall2De.
  Following a data-driven approach, the author proposes five models of anomalous transport.
  These models uses local plasma characteristics, such as the ion sound speed $c_s$, the ion velocity $u_i$, the electron velocity $u_e$, and the Debye length $\lde$.
  Unfortunately, the experimental dataset is sparse, hence the domain of validity of the model is difficult to estimate.
  More precisely, the four \ac{HET} used operate between 1 and 6 \kilo\watt, thus the model may not be usable for smaller thruster.
  
  \vspace{1em}
  The other mechanism enhancing the electron mobility is the secondary electron emission, responsible for a near-wall conductivity \citep{morozov1972,morozov2001, barral2003a}.
  The coupling between the instability and the electron emission has first been studied in \citet{heron2013}, but the mechanism is still not clearly understood.
  
  Consequently, a better understanding of the electron cross-field mobility, the azimuthal instability, and the secondary electron emission is required before being able to model realistically the \ac{HET}.
  
  
\subsection*{Plasma-wall interaction}
\addcontentsline{toc}{subsection}{Plasma-wall interaction}

  The ceramic wall closes the chamber in the radial directions.
  It has been observed in experiments that the nature of the wall can significantly affect the discharge behavior \citep{gascon2003}.
  The primary phenomenon hold responsible for this observation is the electron emission.
  As usually observed in bounded plasmas, a floating sheath forms between the plasma and the dielectric wall.
  The sheath confines the electrons in the plasma and accelerates the ions toward the walls.
  This allows to obtain a flux of electrons equals to the flux of ions, resulting in charge conservation in the plasma, and a neutral flux, or also named zero-net current, to the surfaces.
  
  Due to the relatively high electron energy, the impact of a primary electron can lead to the emission of secondary electrons \citep{barral2003a,villemant2018}.
  The probability of \ac{SEE} depends on the electron impact characteristics (energy, angle) but also of the material\string: some materials are more emitting than others \citep{gascon2003}.
  Ion induced secondary electron emission is much less likely to happen at the range of energy impact \citep{ohya2004}, thus it is neglected compared to the electron induced \ac{SEE}.
  In addition to the near-wall conductivity discussed previously, these secondary electrons are accelerated toward the plasma by the sheath.
  Thus they modify the plasma and the sheath properties.
  Their impact on the electron temperature also affects the ionization rate, which is directly linked to the thruster efficiency.
  
  
  \citet{raitses2005} have observed that the current models of plasma-wall interactions with secondary electron emission cannot reproduce the electron temperature measured experimentally.
  Kinetic effects have been proposed by \citet{sydorenko2007} to explain this discrepancy between the models and the experiments.
  This could explain the differences between the kinetic simulations results and the global models in \citet{croes2017}.   
    
  \vspace{1em}
  In addition to \ac{SEE}, the ion impact energy is large enough to erode the walls by sputtering.
  This erosion is sufficient to be the main limitation of the lifetime of the \ac{HET}s.
  While most aspects of the erosion are well understood, we observe the apparition of  patterns with a typical scale of the order of the millimeter on the eroded surfaces.
  The origin and the possible implications of these erosion striations remain open questions.
  

\subsection*{Three-dimensional physics of the HET}
\label{sec-3Dphi}
\addcontentsline{toc}{subsection}{Three-dimensional physics of the HET}

The physics governing the \ac{HET} is three dimensional\string:
\begin{itemize}
  \item The plasma is accelerated in the axial direction by the electric field, and it is observed experimentally that the axial profile of the magnetic field is responsible for the performance of the thruster.
  \item The chamber walls close the radial dimension. The walls are responsible for most of the plasma losses, both on the particle and energy balances.
  \item The electrons drift in the azimuthal direction, leading to strong instabilities that affect the axial transport.
\end{itemize}

Consequently, when modeling or simulating a \ac{HET}, if one of the direction is not included, a part of the physics will be missing\string:
\begin{itemize}
  \item No axial direction\string: the ionization or the acceleration, as well as the plasma transport, are missing,
  \item No radial direction\string: the wall losses and interactions are missing,
  \item No azimuthal direction\string: the instability is missing. Hence the electron cross-field transport is not well represented.
\end{itemize}

While \ac{3D}-simulations have recently been proposed, they use scaling laws to simulate the system in a reasonable amount of time\citep{taccogna2019a}.
For instance, a reduced geometry is used in \citet{taccogna2018}, or a reduced density is used in \citet{fubiani2018a}.
A \ac{3D} simulation at real scale is not yet accessible.
Hence, we need to be able to rely on \ac{1D} or \ac{2D} simulations.
Consequently, we have to take into account the missing physics or include a model of its effects on the system.
