% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex




\chapter{Parametric study of the dielectric characteristics}
\label{ch-2}

We uses the PIC simulation code described in \cref{ch-1} in order to perform a parametric study over the two aspect of the dielectric walls: the secondary electron emission, and the modification of the electrostatic boundary condition.
We observe there impact on the electron cross-field mobility, and the electron temperature.
A large discrepancy is observed between the sheath model of \cref{sec-sheath} and the PIC simulation results.

\minitoc


% 
% Structure \string:
% 
% {\bf II. Parametric study of the dielectric} 30 pages
% \begin{zzz}
%   This chapter takes the 1rst paper which uses Vivien's results.
% 
%   2.1 Fully metallic wall (no SEE, grounded).
% 
%   2.2 Impact of Dielectric layer without SEE
% 
%   2.3 Impact of SEE with grounded wall
% 
%   2.4 SEE and dielectric in the same time
% 
%   2.5 Discrepancy between $\mean{\Te}$, $\sigma_{PIC}$ and $\sigma_{theo} = \sigma_0 + (1 - \sigma_0) \frac{2 T_e}{\epsilon_0}$
% \end{zzz}

As introduced in \Cref{ch-1}, the \ac{HET} behaviour is dependent of the axial electron transport toward the anode across the magnetic barrier.
Two main phenomena are proposed to enhance the electron mobility,
\begin{itemize}
  \item the azimuthal instability \ac{ECDI}
  \item the electron emission
\end{itemize}
In order to compare quantitatively the relative importance of the two phenomena, we propose to conduct a parametric study on the dielectric wall characteristics.

As highlighted, the \ac{ECDI} rises due to the $E \times B$ electron drift, but saturate thanks to the axial convection model.
Before investigating the time dependent behaviour of the system, we focus in this \Cref{ch-2} on the average values at steady state.
The first section describe the parameters of the simulation, 
while the second section highlight the main characteristics of the simulation result.


\input{Chapitre2/20_parameters}
\input{Chapitre2/21_focus_canonical}
\input{Chapitre2/22_dielectric_layer}
\input{Chapitre2/23_emission_parametric}
\input{Chapitre2/24_parametric_sheath}
\input{Chapitre2/25_diel_and_SEE}
\input{Chapitre2/25_conclusion}
