% !TEX root=/home/tavant/these/manuscript/src/manuscript.tex

\section{Presentation of the study}
  \label{sec-params}
  
  
  
  As introduced in \Cref{ch-1}, the \ac{HET} behavior depends strongly on the axial electron transport toward the anode across the magnetic barrier.
  Two main phenomena are proposed to enhance the electron mobility,
  \begin{itemize}
    \item plasma instabilities and in particular the azimuthal \ac{ECDI}, extensively studied in \cref{ch-5}
    \item the electron induced electron emission from the wall
  \end{itemize}
  In order to compare quantitatively the relative importance of the two phenomena, we propose to conduct a parametric study on the dielectric wall characteristics.
  As highlighted in the introduction and in \cref{ch-5}, the \ac{ECDI} rises due to the $E \times B$ electron drift, but saturates due to both the axial convection which limits the electron heating, and the ion-wave trapping.
  
  The first section describes the parameters of the simulation, 
  while the second section highlights the main characteristics of the base simulation results (electron mobility, plasma potential, electron mobility, etc.).
  The other sections of the chapter present the results of the parametric study on the wall characteristics\string: first we study in \cref{sec-diel_layer} the influence of the dielectric layer, then in \cref{sec-see} the secondary electron emission is analyze, and lastly we combine the two characteristics in \cref{sec-fulldiel}.

  The simulation domain corresponds to the exit plane of the thruster.
  Hence, a neutral pressure $P_n$ of 0.1~mTorr and a plasma density $n_e$ of $\sn{1}{17}$ m$^{-3}$ are used.
  The fixed axial electric field and radial magnetic field are $E_z=\sn{2}{4}\,\volt\per\meter$ and $B_r=200$ G, respectively.
  The rectangular \acs{2D} domain measures $L_r=2$~cm in the radial dimension and $L_{\theta}=0.5$~cm in the azimuthal direction.
  The axial length used for the convection is set to $L_z=1$~cm.
  It is important to note that the results shown in this chapter have been obtained at the beginning of my thesis, before the study of the convection presented in \cref{ch-1}.
  Hence, in this chapter we use the convection model of \citet{lafleur2016a}.
  However, we have validated that the convection model used does not modify the results under the conditions studied.
  The numerical parameters are chosen to respect the stability criterion of \ac{PIC} simulation, and are presented in \Cref{parameters}
  
  \begin{table}[htbp] %PIC parameters
       \centering
       \ra{1.3}
       \caption{\label{parameters} Standard operating and numerical parameters used in the 2D PIC simulations of an HET.  The simulation results are given as representative values.}
       \begin{tabular}{@{}r c c c@{}} 
          \toprule
          {\bf Physical Parameter} & notation & Value & Unit \\
          \midrule
          Gas & & Xenon & - \\
          Domain dimensions & $L_{x} \times L_{y} \times L_{z}$ & $2.0 \times 0.5 \times 1.0$ & [cm$^3$] \\
          Radial magnetic field & $B_{0}$                    & $200$                 & [{G}] \\
          Axial electric field & $E_{0}$                    & $2 \times 10^{4}$     & [{Vm}$^{-1}$] \\
          Mean plasma density & $n_{0}$                    & $3 \times 10^{17}$    & [{m}$^{-3}$] \\
          Initial electron temperature & $\Te_{,0}  $               & $10.0$                 & [{V}] \\
          Initial ion temperature & $T_{i,0}   $               & $0.1$                 & [{V}] \\
          Secondary electron temperature & $T_{see}   $               & $1.0$                 & [{V}] \\
          Neutral gas pressure & $P_{n}     $               & $1.0$                 & [{mTorr}] \\
          Neutral gas temperature & $T_{n}     $               & $300$                 & [{K}] \\
          Neutral gas density & $n_{g}     $               & $3.22 \times 10^{19}$ & [{m}$^{-3}$]\\
          \midrule
          {\bf Simulation Parameter} &  &   &  \\
          
          Time step & $\Delta t  $                      & $4 \times 10^{-12}$ & [{s}] \\
          Cell size & $\Delta x = \Delta y$ & $2 \times 10^{-5}$  & [{m}] \\
          Number of particles per cell & $N/NG      $                      & $80$                & [{part/cell}] \\
          \midrule
          {\bf Typical quantities} &  &  &  \\ 
          Electron plasma frequency & $\omega_{pe}$               & $3.1 \times 10^{10} $  & [rad/s]\\
          Ion plasma frequency & $\omega_{pi}$               & $36 \times 10^{6} $  & [rad/s]\\
          Electron cyclotron frequency & $\omega_{ce}$               &  $3.5\times 10^{9}$  & [rad/s] \\
          Electron Larmor radius & $r_{Le}$                    & 6$\times 10^{-4}$    & [m] \\
          \bottomrule
       \end{tabular}
    \end{table}
  
  
  The simulation is initialized with a uniform density of particles, following a Maxwellian distribution with temperatures $\Te_{,0}$ and $\Ti_{,0}$ for the electrons and the ions, respectively.
  
  